---
title: "Mapview of ecological niche models"
author: "Eric Martiné's Master thesis"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include = FALSE}
library(mapview)
library(raster)
library(sp)
library(scales)

# load occurrences
sp <- read.csv2("data/occ/hastatus_all.csv")

# manipulate df
sp$species <- 1 # 1 for presence (presence-only data)

# convert df to a spatial points df
coordinates(sp) <- c("decimalLongitude", "decimalLatitude")

# load raster layers with predictions
pp.avg   <- raster("output/ensemble/pp_avg_rf-down.tif")
plgm.avg <- raster("output/ensemble/plgm_avg_rf-down.tif")
p26.avg  <- raster("output/ensemble/p26_avg_rf-down.tif")
p45.avg  <- raster("output/ensemble/p45_avg_rf-down.tif")
p60.avg  <- raster("output/ensemble/p60_avg_rf-down.tif")
p85.avg  <- raster("output/ensemble/p85_avg_rf-down.tif")

# define coordinate reference system for sp
projection(sp) <- projection(pp.avg)

# define color palette
cl1 <- viridis_pal(alpha = 1, direction = 1)
```



This site provides extended visualizations of the ecological niche modeling output created in my Master thesis. I present six habitat suitability maps of *Rumex hastatus* for the past (LGM; CHELSA-PMIP3 CCSM4), present (1979-2013; CHELSA bioclim) and future (2061-2080; CHELSA-CMIP5 CCSM4; RCPs 2.6, 4.5, 6.0 and 8.5). They can be interactively viewed using the [mapview](https://r-spatial.github.io/mapview/) package and make up for the restricted view in the printed version of my thesis. Enjoy!



### LGM
```{r echo = FALSE, warning = FALSE}
mapview(plgm.avg, col.regions = cl1(120))
```



### Present
Occurrences of *Rumex hastatus* from GBIF and field work are indicated as blue dots.
```{r echo = FALSE, warning = FALSE}
mapview(pp.avg, col.regions = cl1(120)) + sp
```



### Future RCP 2.6
```{r echo = FALSE, warning = FALSE}
mapview(p26.avg, col.regions = cl1(120))
```



### Future RCP 4.5
```{r echo = FALSE, warning = FALSE}
mapview(p45.avg, col.regions = cl1(120))
```



### Future RCP 6.0
```{r echo = FALSE, warning = FALSE}
mapview(p60.avg, col.regions = cl1(120))
```



### Future RCP 8.5
```{r echo = FALSE, warning = FALSE}
mapview(p85.avg, col.regions = cl1(120))
```



##### Note
The maximum number of pixels has been reduced to 500,000, but the raster files originally have 10,614,240.