---
title: "The South Asian monsoon maintains the disjunction of *Rumex hastatus* between the Western Himalayas and the Hengduan Mountains, Southwest China"
author: "Martiné et al. 2022 (Nord J Bot)"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include = FALSE}
library(mapview)
library(raster)
library(sp)
library(viridis)

# load occurrences
sp <- read.csv2("data/occ/hastatus_all.csv")

# manipulate df
sp$species <- 1 # 1 for presence (presence-only data)

# convert df to a spatial points df
coordinates(sp) <- c("decimalLongitude", "decimalLatitude")

# load raster layers with predictions
present <- raster("output/ensemble/pp_avg_rf-down.tif")
lgm     <- raster("output/ensemble/plgm_avg_rf-down.tif")
rcp2.6  <- raster("output/ensemble/p26_avg_rf-down.tif")
rcp4.5  <- raster("output/ensemble/p45_avg_rf-down.tif")
rcp6.0  <- raster("output/ensemble/p60_avg_rf-down.tif")
rcp8.5  <- raster("output/ensemble/p85_avg_rf-down.tif")

# define coordinate reference system for sp
projection(sp) <- projection(present)

# define color palette
mako <- mako(100, alpha = 1, direction = 1)
```



This site provides extended visualizations of the ecological niche modeling output presented in Martiné et al. (2022). Here, we present six habitat suitability maps of *Rumex hastatus* for the past (LGM; CHELSA-PMIP3 CCSM4), present (1979-2013; CHELSA bioclim) and future (2061-2080; CHELSA-CMIP5 CCSM4; RCPs 2.6, 4.5, 6.0 and 8.5). They can be interactively viewed using the [mapview](https://r-spatial.github.io/mapview/) package and make up for the restricted view in the online/printed version of our paper. Enjoy!



### LGM
```{r echo = FALSE, warning = FALSE}
mapview(lgm, col.regions = mako)
```



### Present
Occurrences of *Rumex hastatus* from GBIF and field work are indicated as blue dots.
```{r echo = FALSE, warning = FALSE}
mapview(present, col.regions = mako) + sp
```



### Future RCP 2.6
```{r echo = FALSE, warning = FALSE}
mapview(rcp2.6, col.regions = mako)
```



### Future RCP 4.5
```{r echo = FALSE, warning = FALSE}
mapview(rcp4.5, col.regions = mako)
```



### Future RCP 6.0
```{r echo = FALSE, warning = FALSE}
mapview(rcp6.0, col.regions = mako)
```



### Future RCP 8.5
```{r echo = FALSE, warning = FALSE}
mapview(rcp8.5, col.regions = mako)
```



##### Note
The maximum number of pixels has been reduced to 500,000, but the raster files originally have 10,614,240.